Sensor Clusterization in D-optimal Design in Infinite Dimensional Bayesian Inverse Problems

### 2020-07-22 paper.tex
Before I delete a bunch of stuff

%-----------------------------------------------------------------------
% Beginning of article-template.tex
%-----------------------------------------------------------------------
%
%    This is a template file for proceedings articles prepared with AMS
%    author packages, for use with AMS-LaTeX.
%
%    Templates for various common text, math and figure elements are
%    given following the \end{document} line.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%    Remove any commented or uncommented macros you do not use.

%    Replace amsproc by the name of the author package.
\documentclass{amsproc}

%    If you need symbols beyond the basic set, uncomment this command.
%\usepackage{amssymb}

%    If your article includes graphics, uncomment this command.
%\usepackage{graphicx}

%    If the article includes commutative diagrams, ...
%\usepackage[cmtip,all]{xy}

%    Include other referenced packages here.
\input{definitions}

%    Update the information and uncomment if AMS is not the copyright
%    holder.
%\copyrightinfo{2009}{American Mathematical Society}

%% \newtheorem{theorem}{Theorem}[section]
%% \newtheorem{lemma}[theorem]{Lemma}

%% \theoremstyle{definition}
%% \newtheorem{definition}[theorem]{Definition}
%% \newtheorem{example}[theorem]{Example}
%% \newtheorem{xca}[theorem]{Exercise}

%% \theoremstyle{remark}
%% \newtheorem{remark}[theorem]{Remark}

@@

% \title[short text for running head]{full title}
\title{A tractable model for D-optimal design in infinite dimensional
  Bayesian inverse problems.}

%    Only \author and \address are required; other information is
%    optional.  Remove any unused author tags.

%    author one information
% \author[short version for running head]{name for top of paper}
\author{Yair Daon}
\address{Courant Institute}
%% \curraddr{}
%% \email{yair.daon@gmail.com}
%% \thanks{}

@@

\subsection{Contribution}
In this work we propose and thoroughly study an analytically tractable
model for understanding D-optimal designs. The initial motivation was
to understand the causes of sensor-clusterization and the end result
is interesting in its own. Specifically, in section \ref{subsec:unit
  length} we suggest a somewhat simplified model for experimental
design that is analytically tractable. In section \ref{section:D and
  grad} we derive a constrained optimization problem for D-optimal
design using Lagrange multipliers. In the case of no model error we
show this constrained optimization problem is in fact a set of
eigenvector-eigenvalue problems \eqref{eq:eigenproblem} and suggest a
natural way for understanding sensor-clusterization in section
\ref{subsub:first attempt}. We explain why this approach fails and
show the reason is that (perhaps surprisingly), all eigenvalues are
equal --- this is done in section \ref{subsub:characterization}. An
important consequence is that we know the value of the best design
criterion without any optimization and which measurements give rise to
it. Practically, we can use this information to seek a design in the
real problem we are interested in and we outline this in section
\ref{section:conclusion}.

@@

\pgfplotstableread{
  Label          prior  $a_1$  $a_2$   $a_3$   $a_4$   $a_5$         $a_6$    topper
  $\ev_1$         0.2    0.8    0.5     0.5    0.4    0.33333333  0.3333333  0.001
  $\ev_2$         0.8    0.2    0.5     0.5    0.4    0.33333333  0.3333333  0.001
  $\ev_3$         2.2    0      0       0      0.2    0.33333333  0.3333333  0.001
  $\ev_4$         3.5    0      0       0      0      0           0          0.001
}\testdata

\begin{figure}
  \begin{tikzpicture}
    \begin{axis}[
        ybar stacked,
        ymin=0,
        ymax=4,
        xtick=data,
        legend style={cells={anchor=east}, legend pos=north west, legend columns=-1},
        reverse legend=false, % set to false to get correct display, but I'd like to have this true
        xticklabels from table={\testdata}{Label},
        xticklabel style={text width=2cm,align=center},
        legend plot pos=right,
        ylabel=prior and posterior precision,
        xlabel=eigenvector,
      ]

@@

      \addlegendentry{prior}
      \addlegendentry{$a_1$}
      \addlegendentry{$a_2$}
      \addlegendentry{$a_3$}
      \addlegendentry{$a_4$}
      \addlegendentry{$a_5$}
      \addlegendentry{$a_6$}   
    \end{axis}
  \end{tikzpicture}
  \caption{Posterior precision per eigenvector. Each measurement
    icreases precision uniformly across the lowest precision
    eigenvectors. We see that $\func_2$ and $\func_3$ are repeated
    measurements, as well as $\func_5$ and $\func_6$.}
  \label{fig:clusterization}
\end{figure}
with the norm constraints on $\meas_j,j=1,...,m$. We show in the
appedix (Lemma \ref{lemma:free}) we can find $\meas_1,...,\meas_m$
such that $\{\eta_i\}_{i=1}^k$ have any value we desire, subject only
to the restriction that we do not change the trace of $\obs^*\obs$, so
that $\sum_{i=1}^k \eta_i = m$. By concavity of $\log$, the highest
increase in the design criterion is gained by increasing
$\lambda_i^{-1} + \sigma^{-2}\eta_i$ where it is small. So, no weight
should be given to (i.e. measurement taken of) the $k$th eigenvector
before $\lambda_i^{-1} + \sigma^{-2}\eta_i \geq \lambda_k^{-1} \forall
i \neq k$. Thus, we should choose $\{\eta_i\}_{i=1}^k$ as follows. We
would increase $\lambda_1^{-1} + \sigma^{-2} \eta_1$ until it equals
$\lambda_2^{-1}$. Then, $\lambda_i^{-1} + \sigma^{-2} \eta_i,i=1,2$ is
increased until $\lambda_i^{-1} + \sigma^{-2} \eta_i =
\lambda_3^{-1},i=1,2$ and so forth.

@@

\subsection{Sensor Clusterization}\label{subsec:clusterization}
The way clusterization can occur is best understood from figure
\ref{fig:clusterization}.

@@

\section{Acknowledgements}
This study was conducted during when I was a PhD student of
Prof. Georg Stadler in New York University's Courant Institute. I
would like to thank him for his great mentorship.

>>>>

\documentclass{amsart}
\input{definitions}

@@

\title[Sensor Clusterization in D-optimal design in infinite
  dimensions]{Sensor Clusterization in D-optimal Design in Infinite
  Dimensional Bayesian Inverse Problems}

\author{Yair Daon}
\address{Courant Institute}
%% \curraddr{}
%% \email{yair.daon@gmail.com}
%% \thanks{}

@@

\subsection{Contribution}
In this work we propose and thoroughly study an analytically tractable
model for understanding D-optimal designs. The initial motivation was
to understand the causes of sensor-clusterization and the end result
is interesting in its own. Specifically, in section \ref{subsec:unit
  length} we suggest a somewhat simplified model for experimental
design that is analytically tractable. In section \ref{section:D and
  grad} we derive a constrained optimization problem for D-optimal
design using Lagrange multipliers. In the case of no model error we
show this constrained optimization problem is in fact a set of
eigenvector-eigenvalue problems \eqref{eq:eigenproblem}. all eigenvalues are
equal --- this is done in section \ref{subsub:characterization}. An
important consequence is that we know the value of the best design
criterion without any optimization and which measurements give rise to
it. Practically, we can use this information to seek a design in the
real problem we are interested in and we outline this in section
\ref{section:conclusion}.

@@

\pgfplotstableread{
  Label    prior  $a_1$  $a_2$   $a_3$   $a_4$   $a_5$         $a_6$    topper
  1         0.2    0.8    0.5     0.5    0.4    0.33333333  0.3333333  0.001
  2         0.8    0.2    0.5     0.5    0.4    0.33333333  0.3333333  0.001
  3         2.2    0      0       0      0.2    0.33333333  0.3333333  0.001
  4         3.5    0      0       0      0      0           0          0.001
}\testdata

\begin{figure}
  \begin{tikzpicture}
    \begin{axis}[
        ybar stacked,
        ymin=0,
        ymax=4,
        xtick=data,
        legend style={cells={anchor=east}, legend pos=north west, legend columns=-1},
        reverse legend=false, % set to false to get correct display, but I'd like to have this true
        xticklabels from table={\testdata}{Label},
        xticklabel style={text width=2cm,align=center},
        legend plot pos=right,
        ylabel=precision --- prior and posterior,
        xlabel=eigenvector,
      ]

@@

      \addlegendentry{prior}
      \addlegendentry{$a_1$}
      \addlegendentry{$a_2$}
      \addlegendentry{$a_3$}
      \addlegendentry{$a_4$}
      \addlegendentry{$a_5$}
      \addlegendentry{$a_6$}   
    \end{axis}
  \end{tikzpicture}
  \caption{Posterior precision per eigenvector. Each measurement $\func_i$
    icreases precision uniformly across the lowest precision
    eigenvectors. We see that $\func_2$ and $\func_3$ are repeated
    measurements, as well as $\func_5$ and $\func_6$.}
  \label{fig:clusterization}
\end{figure}
with the norm constraints on $\meas_j,j=1,...,m$. We show in the
appedix (Lemma \ref{lemma:free}) we can find $\meas_1,...,\meas_m$
such that $\{\eta_i\}_{i=1}^k$ have any value we desire, subject only
to the restriction that we do not change the trace of $\obs^*\obs$, so
that $\sum_{i=1}^k \eta_i = m$. By concavity of $\log$, the highest
increase in the design criterion is gained by increasing
$\lambda_i^{-1} + \sigma^{-2}\eta_i$ where it is small. So, no weight
should be given to (i.e. measurement taken of) the $k$th eigenvector
before $\lambda_i^{-1} + \sigma^{-2}\eta_i \geq \lambda_k^{-1} \forall
i \neq k$. Thus, we should choose $\{\eta_i\}_{i=1}^k$ as follows. We
would increase $\lambda_1^{-1} + \sigma^{-2} \eta_1$ until it equals
$\lambda_2^{-1}$. Then, $\lambda_i^{-1} + \sigma^{-2} \eta_i,i=1,2$ is
increased until $\lambda_i^{-1} + \sigma^{-2} \eta_i =
\lambda_3^{-1},i=1,2$ and so forth.

@@

\subsection{Sensor Clusterization}\label{subsec:clusterization}
The way clusterization can occur is best understood from figure
\ref{fig:clusterization}. We see that each measurement increases
precision (reduces uncertainty) only for the eigenvectors of lowest
precision. If the precision in these is lower than the precision for
the next eigenvector, a repeated measurement is taken.

@@

\section{Acknowledgements}
This study is a part of my PhD thesis \cite{mine} which was written
under the instruction of Prof. Georg Stadler in New York University's
Courant Institute. I would like to thank him for his great mentorship.
